\documentclass[preprint,showkeys,nofootinbib]{revtex4-1}


% linking references
\usepackage{hyperref}
\hypersetup{
  breaklinks=true,
  colorlinks=true,
  linkcolor=blue,
  urlcolor=cyan,
}


% general physics / math packages and commands
\usepackage{physics,amsmath,amssymb,braket,dsfont}
\renewcommand{\t}{\text} % text in math mode
\newcommand{\f}{\dfrac} % shorthand for fractions
\newcommand{\p}[1]{\left(#1\right)} % parenthesis
\renewcommand{\sp}[1]{\left[#1\right]} % square parenthesis
\renewcommand{\set}[1]{\left\{#1\right\}} % curly parenthesis
\newcommand{\bk}{\braket} % shorthand for braket

\renewcommand{\d}{\text{d}}
\newcommand{\g}{\text{g}}
\newcommand{\e}{\text{e}}
\newcommand{\x}{\text{x}}
\newcommand{\y}{\text{y}}
\newcommand{\z}{\text{z}}

\renewcommand{\c}{\hat{c}}
\newcommand{\n}{\hat{n}}

\newcommand{\A}{\mathcal{A}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\G}{\mathcal{G}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\K}{\mathcal{K}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\N}{\mathcal{N}}
\renewcommand{\O}{\mathcal{O}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\Q}{\mathcal{Q}}
\renewcommand{\S}{\mathcal{S}}
\newcommand{\U}{\mathcal{U}}

\newcommand{\1}{\mathds{1}}

\newcommand{\mA}{m_{\text{A}}} % symbol for the mass of an atom


% "left vector" arrow; requires tikz package
\newcommand{\lvec}[1]
{\reflectbox{\ensuremath{\vec{\reflectbox{\ensuremath{#1}}}}}}


% figures
\usepackage{graphicx} % for figures
\usepackage{grffile} % help latex properly identify figure extensions
\graphicspath{{./figures/}} % set path for all figures
\usepackage[caption=false]{subfig} % subfigures (via \subfloat[]{})


% inline lists
\usepackage[inline]{enumitem}


% for feynman diagrams
\usepackage{tikz,tikz-feynman}
\tikzset{
  baseline = (current bounding box.center)
}
\tikzfeynmanset{
  compat = 1.1.0,
  every feynman = {/tikzfeynman/small}
}
\newcommand{\shrink}[1]{\scalebox{0.8}{#1}} % for smaller diagrams


% color definitions (used in a figure)
\usepackage{xcolor}
\definecolor{lightblue}{RGB}{31,119,180}
\definecolor{orange}{RGB}{255,127,14}
\definecolor{green}{RGB}{44,160,44}
\definecolor{lightred}{RGB}{214,39,40}


% proper coloring inside math environment
\makeatletter
\def\mathcolor#1#{\@mathcolor{#1}}
\def\@mathcolor#1#2#3{
  \protect\leavevmode
  \begingroup
    \color#1{#2}#3
  \endgroup
}
\makeatother
\newcommand{\bmu}{\mathcolor{lightblue}{\mu}}
\newcommand{\onu}{\mathcolor{orange}{\nu}}
\newcommand{\grho}{\mathcolor{green}{\rho}}
\newcommand{\re}{\mathcolor{lightred}{\text{e}}}


% leave a note in the text, visible in the compiled document
\newcommand{\note}[1]{\textcolor{red}{#1}}

% for strikeout text
% normalem included to prevent underlining titles in the bibliography
\usepackage[normalem]{ulem}


\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\green}[1]{\textcolor{green}{#1}}


\begin{document}

\section*{Referee 2}

We thank the referee for taking the time to read and reconsider our
revised manuscript.  Concerning the comments:

\blue{I read the replies from the authors and other report and
  recommend the publication.}

\blue{There are a few discussions on ``renormalization'' schemes in
  the article and in Referee 1's report.  Let me comment on the scheme
  in the manuscript. The scheme used here (more precisely
  ``regularization'' scheme) is a quite standard and has been commonly
  used in many-body studies since the beginning of many-body
  diagrammatic calculations. It is based on a k-space ``pseudo''
  potential.  From the point of view of low energy few-body physics
  studied here, it is indeed equivalent to the other well known
  standard real space ``differential pseudo'' potential Referee A
  might have in mind (I speculate that what he/she meant by ``pseudo
  potential''). But more importantly, it can be easily and
  straightforwardly generalized to arbitrary dimensions and can be
  integrated into studies of complex/sophisticated collective
  many-body effects associated with Fermi surfaces and/or sound waves
  in symmetry breaking states.}

We thank the referee for their recommendation to publish our
manuscript, and for their input on the regularization scheme in our
manuscript.  In particular, we thank the referee for pointing out that
our approach to regularizing the two-body delta-function interaction
is a standard technique in many-body studies, equivalent to another
common technique based on a regularized real-space ``differential
pseudo-potential''.

\end{document}
